The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-28 paper/ms.tex
Improving plots
figures

\label{sec:off-center}
\begin{figure}
  \includegraphics[scale=0.3]{f8.eps}
  \caption{The two small circles show the two different spherical
    off-centered emitting regions with respect to the larger spherical
    gas distribution. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (outwards the
    page). In order to study a possible anysotropy we place an
    observer along the the $\hat{\j}$ direction. The vector
    $\hat{k}_{\rm out}$ represents the outgoing direction of an
    escaping \ly photon. {\bf Si el observador esta en j, entonces las
    dos esferas no deberian estar sobre el eje k? Lo mejor es ademas
    hacer las dos circulos pequenos punteados}
    \label{fig:OCspheres}} 
\end{figure}

Rotation breaks the spherical symmetry of the static model and
introduces a prefered axis

The raw data from the model with homogeneous radiation sources allows
to study the effect of radiation sources distributed with a different
symmetry than the gas. We can select photons emitted in off-centered spheres 
with respect to the gas distribution and check whether this produces
asymmetries in the line.

Figure \ref{fig:OCspheres} shows the two spherical regions we
define to test for this effect. Each has a radius of $0.5$R and can
have two possible centers positions $C$ along the $\hat{\j}$ direction:
$\pm C\hat{\i}$. We also place an observer along the $\hat{\j}$
direction, such that the emitting sphere centered on $+C\hat{\j}$ moves
away from the observer and the sphere centered on $-C\hat{\j}$ moves
towards the observer.

We study first the angular deviations of the outgoing photons with respect
to an isotropic flux. We follow \cite{Zheng2013} to estimate the flux
as a function of the angle $\Theta$ formed by the outgoing photons and
the observer. This is expressed by

\begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation} 
%
where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in a angular bin $\Delta
\Theta$. This definition satisfies the condition
$\int_{-1}^{1}F(\mu)d\mu/2=1$.

@@

@@

\begin{figure*}
\includegraphics[scale=0.3]{f12.eps}
\caption{Three-Peak profiles for different resolutions:Low (Solid), medium(dashed), high(doted), 
   \label{fig:3p_res}} 
\end{figure*}

>>>>

\label{sec:off-center}
\begin{figure}
  \includegraphics[scale=0.3]{f8.eps}
  \caption{The two small circles show the two different spherical
    off-centered emitting regions with respect to the larger spherical
    gas distribution. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (outwards the
    page). In order to study a possible anysotropy we place an
    observer along the the $\hat{\j}$ direction. The vector
    $\hat{k}_{\rm out}$ represents the outgoing direction of an
    escaping \ly photon. {\bf Si el observador esta en j, entonces las
    dos esferas no deberian estar sobre el eje k? Lo mejor es ademas
    hacer las dos circulos pequenos punteados.}
    \label{fig:OCspheres}} 
\end{figure}

@@

Rotation breaks the spherical symmetry of the static model and
introduces the rotation axis as a preferred direction. This motivates
us to study the anisotropy of the outgoing photons. In order to study
possible deviations with respect to an isotropic flux we follow
\cite{Zheng2013} to estimate the flux as a function of the angle
$\Theta$ formed by the outgoing photons and the observer. Figure
\ref{fig:OCspheres} presents a geometric scheme to clarify the
definition of all relevant directions in the problem.

An estimator for the anysotropy is represented by
%
\begin{equation}
F(\mu) = \frac{2\Delta N}{N\Delta \mu}, 
\end{equation} 
%
where $\mu=\cos\Theta$, $N$ is the total number of outgoing photons,
$\Delta N$ is the number of photons in a angular bin $\Delta
\Theta$. This definition satisfies the condition
$\int_{-1}^{1}F(\mu)d\mu/2=1$.  With this definitions, the isotropic
emission is characterized by a flat $F(\mu)$ distribution.

Figure \ref{fig:OCspheres} presents the results for the $F(\mu)$
distribution for an sphere with $\tau_{\rm H}=10^{7}$ and $V_{\rm
  max}=200$\kms. The dashed and dotted lines represent the homogeneous
and central source distribution, respectively. This shows that the
level of anisotropy induced by rotation does not surpasses the $5\%$
level. We performed the same test with all the models and we do not
fina any significant anisotropic effect.

We explore other kind of anisotropy by study the effect
of radiation sources distributed with a different symmetry than the
gas. To this end we select a subset of the photons in the homogeneous
models such as they are emitted from off-centered spheres with respect
to the gas distribution.

Figure \ref{fig:OCspheres} shows the two spherical regions we
define to test for this effect. Each has a radius of $0.5R$, where $R$
is the radius of the gaseus sphere. Provided that there is an observer
located along the $\hat{j}$ direction, we pick two possible positions
to center the spheres along the $\hat{k}$ axis: $\pm C\hat{k}$. In
this configuration the emitting sphere centered on $+C\hat{k}$ moves
away from the observer and the sphere centered on $-C\hat{j}$ moves
towards the observer.

%JEFR

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.3]{f12.eps}
\end{center}
\caption{Three-Peak profiles for different resolutions:Low (Solid), medium(dashed), high(doted), 
   \label{fig:3p_res}} 
\end{figure}
